Towards caring 15-minute neighbourhoods

### 2024-07-06 data/01-census-and-traveltimes.qmd
current draft version - added some comments from discussion 2 weeks ago with the team.

## Transit travel times

@@

@@

@@

save("ttm_care_TRANSIT_parcel1", file = "parcel-ttm/ttm_care_TRANSIT_parcel1.rda")
rm("ttm_care_TRANSIT_parcel1")
```

>>>>

##Transit travel times

@@

```{r}
load("parcel-ttm/ttm_care_TRANSIT_parcel1_1.rda")
load("parcel-ttm/ttm_care_TRANSIT_parcel1.rda")

ttm_care_TRANSIT_parcel1|> summary()
ttm_care_TRANSIT_parcel1_1 |> summary()
```

@@

for (i in 1:num_chunks){
  Orig_chunk <- get_chunk(origins_chunks, i)
  ttm_chunk <- travel_time_matrix(r5r_core = r5_HAM,
                          origins = Orig_chunk,
                          destinations = dest,
                          mode = c("TRANSIT","WALK"),
                          max_walk_time = 15,
                          departure_datetime = as.POSIXct(strptime("08-06-2023 08:00:00", # 12 GMT is 8am in Toronto (EDT)
                                 format = "%d-%m-%Y %H:%M:%S")),
                          max_trip_duration = 30)

@@

save("ttm_care_TRANSIT_parcel1", file = "parcel-ttm/ttm_care_TRANSIT_parcel1_1.rda")
rm("ttm_care_TRANSIT_parcel1_1")
```

### 2024-07-06 paper/Manuscript.qmd
current draft version - added some comments from discussion 2 weeks ago with the team.

The 15-minute neighbourhood is a concept in planning that promotes urban spaces that are responsive to human needs and environmental sensibilities. These neighbuorhoods aim to accomplish this by ensuring that most daily necessities are not further away than a 15 minutes active trip [@Allam2022]. In practice, 15-minute neighborhoods are a form of normative accessibility, [@paez_measuring_2012], and therefore related to accessibility analysis, an increasingly important tool that planners use to foster just and sustainable cities [@vale2023accessibility; @handyAccessibilityIdeaWhose2020]. Both the 15-minute neighborhood and accessibility measures are flexible enough to consider all destination types holistically, however, gendered examinations have been lacking in the literature. For instance, accessibility analyses have historically been employment-centric even when adopting a gendered perspective [@paez_jobs_2024].

To address this gender bias, this study investigates the 15-minute neighbourhood through the lens of Mobility of Care [@@sanchezdemadariagaMobilityCareIntroducing2013]. This framework emphasizes the importance of travel related to unpaid work (care trips) in contrast to the better-studied travel to employment and leisure [@lawWomenTransportNew1999; @cresswell_gendered_2008; @Oestergaard1992; @levy1991towards; @levy2013travel]. While these trip types (work, care, and leisure) are essential, care trips are often relatively shorter-distance, proximate to residential/work/school, and comprise approximately 30% of adults’ daily trips [@sanchezdemadariagaMeasuringMobilitiesCare2019; @ravensbergen2023exploratory; @mejia2021mobility], thus fitting neatly within the concept of 15-minute neighbourhoods.

@@

Caring is one of the most fundamental activities in societies, since it consists of numerous activities that allow them to thrive. Caring activities are those that strive to meet the physical, psychological, and emotional needs of others [@ilo_care_2018]. Yet, it is one of the most unequal, undervalued, and even devalued activities worldwide. Traditionally, caring activities have been borne on women’s shoulders. Though women today attain higher educational levels and tend to work out of home more than ever before, the 'Second Shift' remains mostly women’s work  in all industrial societies [@hayden_grand_2000; @hochschild_second_2012]. According to @ilo_care_2018, women and girls perform more than three-quarters of the total amount of unpaid care, a gender gap that varies geographically [@RN5]. In Canada, adult women complete 1.9 hours, on average, more of unpaid care than men every day [@RN4].

@@

Care also has important implications for spatial and transportation planning. Indeed, researchers from various fields have highlighted that western modern industrial societies have imposed a physical separation of the private sphere from the public one, splitting production and reproduction, public and private spaces or simply work and home, concentrating on the economic outcome of being mobile [@cresswell_gendered_2008; @lawWomenTransportNew1999; @levy2013travel; @little_gender_1994; @tronto_toward_1990]. The man with legal rights, paid labour public sphere and woman in the private sphere, dependent, with family duties, personal relations and unpaid labour [@tronto_toward_1990]. In this line, @cresswell_gendered_2008 described how masculinity was related to mobile and active, whereas femininity to static. As an example of this dichotomy, transport planning historically framed non-work/school trips as 'non-mandatory' activities, downgrading these activities in comparison to work. In more recent years, planners have begun to resist this spatial separation of the public and private sphere to promote for sustainable cities. Proximity planning has become more normalized, at popular example of which is the 15-minute neighbourhood, in which residents can reach all necessary destinations within a 15-minute walk. The 15-minute neighbourhood concept, however, has yet to directly focus on care.

While much care labour takes place in the private, and feminised sphere, completing care activities requires one to be mobile. In other words: caring for oneself and others requires trips to, amongst other places, grocery stores, day cares, elder care, and health care destinations.

Women have consistently been found to complete more mobility of care trips than men. In one study, mobility of care comprised 32% of women’s daily trips compared to 28% of men’s. While this gap was significant, it was found to be far greater in lower income households where women complete 20% more care trips than men [@ravensbergen2023exploratory]. This gendered division in mobility of care is perhaps unsurprising as women tend to complete a disproportionate amount of household-serving labour, such as caring for children and other dependents, preparing meals, cleaning, and running errands, when compared to men [@RN4]. This gender gap varies geographically [@RN5]. In Canada, adult women complete 1.9 hours, on average, more of unpaid care than men every day [@RN4]. This labour is essential, and a large component of daily life.

@@

`r word_comment("Good 15 minute city example, but what about feminist 15 minute cities? It's novel but movements exists such as https://x.com/brenttoderian/status/1800371515877384527?s=48&t=QI0WSvV_FDb82ZGeLdJ9lQ", " ")`

@@

In the last decades, the need for more sustainable, healthier, and liveable cities has received more attention. Planners and policy makers have proposed different alternatives where residents reach “essential activities” within walkable or cycling distances, reducing the need for using motorised transportation modes. The 15-minutes cities, 20-minutes or x-minutes cities, have been long under the spotlight. This approach has also received the name of Chrono-urbanism or the “cities of proximity” [@logan_xminute_2022; @moreno_introducing_2021].

In the international context, there are different examples that highlight the importance of good access to different services and amenities within walkable distances. Probably one of the first cities to adopt the proximity approach was Portland. The Portland Plan [@city_of_portland_20minute_2010] was adopted by the City Council on April 25, 2012 aiming at fostering an inclusive city development for the following 30 years. The plan is based on the following principles: prosperity, education, health, and equity. The progress report states that equity should be achieved, an Office of Equity and Human Rights was established focusing on equitable service delivery to all residents. Nonetheless the progress report only measures progress on topics related to racial equity or people with disabilities [@portland_government_portland_2017].

@@

Given that almost one third of daily trips are for care purposes [@sanchezdemadariagaMobilityCareIntroducing2013], it is important to plan for mobility of care. There are also equity considerations to consider: as discussed, women, and especially low-income women, are particularly in charge of these duties and therefore, complete this travel more than men. Planning for mobility of care may also warrant different considerations because mobility of care trip characteristics differ from other trips, notably those of the commute to work. For instance, many of these trips are made through trip-chains, i.e., when a non-work-related stop is made during the commute. Women have been found to do so more than men, which is understood as being due to their need to balance unpaid-household serving care and paid employment (e.g., picking up groceries or children on the way home from work) [@ravensbergen2023exploratory; @scheinerWomenComplexDaily2015].

Further, compared to the trip to work, mobility of care trips are more frequently completed by car and by foot, and less frequently done by transit or bicycle [@ravensbergen2023exploratory]. Evidence for why this modal difference is observed exists. For instance, it is possible that walking is more common for care than for work trips because care trips tend to be short [@ravensbergen2023exploratory]. In other words, if care destinations are closer to the home, it is more likely that these destinations are walkable. Ample literature examines the benefits and barriers to walking care destinations, such as schools (e.g., [@RN7;@RN8;@RN9]) and grocery stores (e.g., [@RN10;@RN11]). Little of this work uses the mobility of care framework. Instead, it tends to consider singular care destinations in research focusing on walkability.

In car dependent cities, cycling commute rates tend to be low. Emerging evidence has found that they are even lower for care trips than for work trips. For instance, in Montréal it is estimated that 2% of work trips completed by adults are done by bicycle, while only 1.1% of care trips are done using this sustainable travel mode [@ravensbergen2023exploratory]. Qualitative research has also found that in car-dependent contexts, many consider it inappropriate and unsafe to conduct escort trips by bicycle [@ravensbergenVelomobilitiesCareLowcycling2020; @sersliRidingAloneTogether2020]. Then again, other studies have uncovered the joys inherent in travelling by bicycle with children [@RN14]. This qualitative evidence has also found that the bicycle is excellent for trip-chaining owning to its flexibility and ease of parking, and that grocery shopping can be done by bicycle, though this can require some additional materials (e.g., paniers) and competencies (e.g., knowing where to put your groceries)[@ravensbergenVelomobilitiesCareLowcycling2020]. Research in the Netherlands, a high-cycling context, has found that parents can and do use their bicycles to complete mobilities of care. Indeed, one study compared women with children’s bicycle behaviours to those without children and found that the having a child did not change the amount of cycling done, but the characteristics of cycling trips: mothers’ trips tended to center around their childrens’ needs [@RN15]. Taken together, it is evident that the bicycle has potential to serve mobility of care: it is flexible, low-cost, and used for these trips in many contexts. Other barriers to this travel mode seems to exist in low-cycling contexts.

@@

## Case study context
In Canada, women have become more educated and have an achieved an increased participation in the labour market [@government_of_canada_gender_2023]. In fact, the educational level of women has surpassed most men [@government_of_canada_women_2023]. Reports observe that the gender pay gap has narrowed but disparities persist [@drolet_intersectional_2023;@pay_equity_office_gender_2023]. According to the statistics, in Ontario between 1998 to 2022 the gender gap narrowed but still women make 87 cents on average for every dollar made by a man [@pay_equity_office_gender_2023]. All reports observe that it affects women differently, women with disabilities, immigrants, indigenous or racialized suffer especially from the gender pay gap. Similarly to other countries worldwide, the occupational segregation remains and women are segregated into lower paid job classes and there is a dominance of women in minimum wage jobs [@drolet_intersectional_2023]. Furthermore, women are underemployed, and make up most part-time work. In this respect, the lack of childcare alternatives enforces this obligatory part-time work [@equal_pay_coalition_myths_2022]. All researchers and organisations agree that an intersectional approach is of utmost importance to better plan policies to enforce gender equality.

@@

Here we will describe the estimated 15-minute walk travel times using {r5r}, from all residential parcel points to all care destinations assuming default walking speed (3.6km/hr) and OSM road network for Hamilton. **Provide summary statistics.**

@@

Accessibility per category @fig-Fig4:
```{r plot-figure4, out.width=600, out.height=600}
#| label: fig-Fig4
#| fig-cap: "The number of care destinations that can be reached within 15 min walk per care category for a median parcel in each DA. Scales are in quartiles. These are four of five inputs into the superclusters. Basemap shapefiles are retrieved from the 2021 Canadian census [@governmentofcanadaCensusPopulation2023], the Open Data Hamilton Portal [@opendatahamiltonCityBoundary2023] and the USGS [@greatlakesUSGS2010]."
knitr::include_graphics(glue::glue(here::here(), "/figures/percats_copp_plot.png"))
```

Diversity @fig-Fig5:
```{r plot-figure5, out.width=600, out.height=600}
#| label: fig-Fig5
#| fig-cap: "The diversity measure (div) based on the proportion of care category spatial accessibility (figure 4). Scale is in tertiles. The fifth input into the superclusters. Basemap shapefiles are retrieved from the 2021 Canadian census [@governmentofcanadaCensusPopulation2023], the Open Data Hamilton Portal [@opendatahamiltonCityBoundary2023] and the USGS [@greatlakesUSGS2010]."
knitr::include_graphics(glue::glue(here::here(), "/figures/all_cats_entropy_copp_plot.png")) 
```

Superclusters based on accessibility per category and diversity (the two above figures). 5 clusters are identified, see their dendrogram (right) and grid map (left) in @fig-Fig6 :

@@

To further visualize supercluster membership, we spatially demonstrate which supercluster best describes each parcel in @fig-Fig8 (top plot): the median parcel's supercluster membership per DA is tabulated and the majority membership is represented. Visually, the super clusters closely follow the quartile split of the accessibility to care destinations (all categories combined) and tertile split of the diversity scores (visualised in @fig-Fig5).

@@

#Conclusions and Discussion

There seems to be a spatial mismatch where dwelling availability and affordability play an important role? (NOTE: LMD has have questions about the results) Are there social housing programs for lower income households?

>>>>

The 15-minute neighbourhood is a concept in planning that promotes urban spaces that are responsive to human needs and environmental sensibilities. These neighbuorhoods aim to accomplish this by ensuring that most daily necessities are not further away than a 15 minutes active trip [@Allam2022]. In practice, 15-minute neighborhoods are a form of normative accessibility [@paez_measuring_2012], and therefore related to accessibility analysis, an increasingly important tool that planners use to foster just and sustainable cities [@vale2023accessibility; @handyAccessibilityIdeaWhose2020]. Both the 15-minute neighborhood and accessibility measures are flexible enough to consider all destination types holistically, however, gendered examinations have been lacking in the literature. For instance, accessibility analyses have historically been employment-centric even when adopting a gendered perspective [@paez_jobs_2024].

To address this gender bias, this study investigates the 15-minute neighbourhood through the lens of Mobility of Care [@sanchezdemadariagaMobilityCareIntroducing2013]. This framework emphasizes the importance of travel related to unpaid work (care trips) in contrast to the better-studied travel to employment and leisure [@lawWomenTransportNew1999; @cresswell_gendered_2008; @Oestergaard1992; @levy1991towards; @levy2013travel]. While these trip types (work, care, and leisure) are essential, care trips are often relatively shorter-distance, proximate to residential/work/school, and comprise approximately 30% of adults’ daily trips [@sanchezdemadariagaMeasuringMobilitiesCare2019; @ravensbergen2023exploratory; @mejia2021mobility], thus fitting neatly within the concept of 15-minute neighbourhoods.

@@

Caring is one of the most fundamental activities in societies, since it consists of numerous activities that allow them to thrive. Caring activities are those that strive to meet the physical, psychological, and emotional needs of others [@ilo_care_2018]. Yet, it is one of the most unequal, undervalued, and even devalued activities worldwide. Traditionally, caring activities have been borne on women’s shoulders [@hayden_grand_2000; @hochschild_second_2012]. According to @ilo_care_2018, women and girls perform more than three-quarters of the total amount of unpaid care, a gender gap that varies geographically [@RN5].

@@

Care also has important implications for spatial and transportation planning. Indeed, researchers from various fields have highlighted that western modern industrial societies have imposed a physical separation of the private sphere from the public one, splitting production and reproduction, public and private spaces or simply work and home, concentrating on the economic outcome of being mobile [@cresswell_gendered_2008; @lawWomenTransportNew1999; @levy2013travel; @little_gender_1994; @tronto_toward_1990]. The man with legal rights, paid labour public sphere and woman in the private sphere, dependent, with family duties, personal relations and unpaid labour [@tronto_toward_1990]. In this line, @cresswell_gendered_2008 described how masculinity was related to mobile and active, whereas femininity to static. As an example of this dichotomy, transport planning historically framed non-work/school trips as 'non-mandatory' activities, downgrading these activities in comparison to work. In more recent years, planners have begun to resist this spatial separation of the public and private sphere to promote for sustainable cities. Proximity planning has become more normalized, at popular example of which is the 15-minute neighbourhood, in which residents can reach all necessary destinations within a 15-minute walk. The 15-minute neighbourhood concept, however, has yet to foreground care.

While much care labour takes place in the private and feminised sphere, completing care activities requires one to be mobile. In other words: caring for oneself and others requires trips to, amongst other places, grocery stores, day cares, elder care, and health care destinations.

@@

`r word_comment("TO ADD: some good feminist 15 minute cities. It's novel but movements exists in the Canadian context i.e., https://x.com/brenttoderian/status/1800371515877384527?s=48&t=QI0WSvV_FDb82ZGeLdJ9lQ. Also discuss Barcelona and Bogota (care blocks)", " ")`

@@

In the last decades, the need for more sustainable, healthier, and liveable cities has received more attention. Planners and policy makers have proposed different alternatives where residents reach “essential activities” within walkable or cycling distances, reducing the need for using motorised transportation modes. The 15-minutes cities or "x"-minutes cities, have been long under the spotlight. This approach has also received the name of Chrono-urbanism or the “cities of proximity” [@logan_xminute_2022; @moreno_introducing_2021].

In the international context, there are different examples that highlight the importance of good access to different services and amenities within walkable distances. Probably one of the first cities to adopt the proximity approach was Portland. The Portland Plan [@city_of_portland_20minute_2010] was adopted by the City Council on April 25, 2012 aiming at fostering an inclusive city development based on prosperity, education, health, and equity for the following 30 years. The progress report states that equity should be achieved, an Office of Equity and Human Rights was established focusing on equitable service delivery to all residents. Nonetheless the progress report only measures progress on topics related to racial equity or people with disabilities [@portland_government_portland_2017]. `r word_comment("NOTE TO SELF: And so what? Is this a research gap?", " ")`

@@

Given that almost one third of daily trips are for care purposes [@sanchezdemadariagaMobilityCareIntroducing2013], it is important to plan for mobility of care. There are also equity considerations to consider; women, and especially low-income women, are particularly in charge of these duties and therefore, complete this travel more than men. Planning for mobility of care may also warrant different considerations because mobility of care trip characteristics differ from other trips, notably those of the commute to work. For instance, many of these trips are made through trip-chains, i.e., when a non-work-related stop is made during the commute. Women have been found to do so more than men, which is understood as being due to their need to balance unpaid-household serving care and paid employment (e.g., picking up groceries or children on the way home from work) [@ravensbergen2023exploratory; @scheinerWomenComplexDaily2015].

Further, compared to the trip to work, mobility of care trips are more frequently completed by foot, and less frequently done by transit or bicycle [@ravensbergen2023exploratory]. Further, evidence suggests that walking is more common for care than for work trips because care trips tend to be short [@ravensbergen2023exploratory]; if care destinations are closer to the home, it is more likely that these destinations are walkable. Ample literature examines the benefits and barriers to walking care destinations, such as schools (e.g., [@RN7;@RN8;@RN9]) and grocery stores (e.g., [@RN10;@RN11]). However, little of this work uses the mobility of care framework. Instead, they tend to consider singular care destinations in research focusing on walkability.

`r word_comment("TO ADD: Replace the following three paragrapgs with a more elaborated discussion on walking as the primary mode for 15-min cities and how it overlaps with mobility of care. ", ".")`
In car dependent cities, cycling commute rates tend to be low. Emerging evidence has found that they are even lower for care trips than for work trips. For instance, in Montréal it is estimated that 2% of work trips completed by adults are done by bicycle, while only 1.1% of care trips are done using this sustainable travel mode [@ravensbergen2023exploratory]. Qualitative research has also found that in car-dependent contexts, many consider it inappropriate and unsafe to conduct escort trips by bicycle [@ravensbergenVelomobilitiesCareLowcycling2020; @sersliRidingAloneTogether2020]. Then again, other studies have uncovered the joys inherent in travelling by bicycle with children [@RN14]. This qualitative evidence has also found that the bicycle is excellent for trip-chaining owning to its flexibility and ease of parking, and that grocery shopping can be done by bicycle, though this can require some additional materials (e.g., paniers) and competencies (e.g., knowing where to put your groceries)[@ravensbergenVelomobilitiesCareLowcycling2020]. Research in the Netherlands, a high-cycling context, has found that parents can and do use their bicycles to complete mobilities of care. Indeed, one study compared women with children’s bicycle behaviours to those without children and found that the having a child did not change the amount of cycling done, but the characteristics of cycling trips: mothers’ trips tended to center around their childrens’ needs [@RN15]. Taken together, it is evident that the bicycle has potential to serve mobility of care: it is flexible, low-cost, and used for these trips in many contexts. Other barriers to this travel mode seems to exist in low-cycling contexts.

@@

## Case study context

In Canada, women have become more educated and have an achieved an increased participation in the labour market [@government_of_canada_gender_2023]. In fact, the educational level of women has surpassed most men [@government_of_canada_women_2023]. Reports observe that the gender pay gap has narrowed but disparities persist [@drolet_intersectional_2023;@pay_equity_office_gender_2023]. According to the statistics, in Ontario between 1998 to 2022 the gender gap narrowed but still women make 87 cents on average for every dollar made by a man [@pay_equity_office_gender_2023]. All reports observe that it affects women differently, women with disabilities, immigrants, indigenous or racialized suffer especially from the gender pay gap. Similarly to other countries worldwide, the occupational segregation remains and women are segregated into lower paid job classes and there is a dominance of women in minimum wage jobs [@drolet_intersectional_2023]. Furthermore, women are underemployed, and make up most part-time work. In this respect, the lack of childcare alternatives enforces this obligatory part-time work [@equal_pay_coalition_myths_2022]. All researchers and organisations agree that an intersectional approach is of utmost importance to better plan policies to enforce gender equality.

@@

Here we will describe the estimated 15-minute walk travel times using {r5r}, from all residential parcel points to all care destinations assuming default walking speed (3.6km/hr) and OSM road network for Hamilton. `r word_comment("TO ADD: add summary statistics", " ")`

@@

Accessibility per category @fig-Fig4. The concentration of opportunities for all category types is concentrated in Hamilton Central - with the highest concentration being in the lower city and pockets of the high concentration on the mountain `r word_comment("(TO ADD: The escarpment line)", " ")`. Grocery-centric opportunities are most concentrated, followed by dependent-centric and health-centric. Errand-centric is the most sprawled.

```{r plot-figure4, out.width=600, out.height=600}
#| label: fig-Fig4
#| fig-cap: "The number of care destinations that can be reached within 15 min walk per care category for a median parcel in each DA. Scales are in quartiles. These are four of five inputs into the superclusters. Basemap shapefiles are retrieved from the 2021 Canadian census [@governmentofcanadaCensusPopulation2023], the Open Data Hamilton Portal [@opendatahamiltonCityBoundary2023] and the USGS [@greatlakesUSGS2010]."
knitr::include_graphics(glue::glue(here::here(), "/figures/percats_copp_plot.png"))
```
Diversity @fig-Fig5. Concentrated in the downtown core.
```{r plot-figure5, out.width=600, out.height=600}
#| label: fig-Fig5
#| fig-cap: "The diversity measure (div) based on the proportion of care category spatial accessibility (figure 4). Scale is in tertiles. The fifth input into the superclusters. Basemap shapefiles are retrieved from the 2021 Canadian census [@governmentofcanadaCensusPopulation2023], the Open Data Hamilton Portal [@opendatahamiltonCityBoundary2023] and the USGS [@greatlakesUSGS2010]."
knitr::include_graphics(glue::glue(here::here(), "/figures/all_cats_entropy_copp_plot.png")) 
```

Superclusters based on accessibility per category and diversity (the two above figures). 5 clusters are identified, see their dendrogram (right) and grid map (left) in @fig-Fig6 `r word_comment("change colours of SC to match the following plots", ":")`.

@@

To further visualize supercluster membership, we spatially demonstrate which supercluster best describes each parcel in @fig-Fig8 (top plot): the median parcel's supercluster membership per DA is tabulated and the majority membership is represented. Visually, the super clusters closely follow the quartile split of the accessibility to care destinations (all categories combined) and tertile split of the diversity scores (visualised in @fig-Fig5) `r word_comment("AN IDEA DISCUSSED: Overall, in @fig-Fig8 there are many pockets of good/great care accessibility+diversity of opportunities Hamilton. These are objectively caring neighbourhoods. However, people may subjectively disagree... ", ".")`.

@@

 `r word_comment("IDEAS DISCUSSED: regarding @fig-Fig9 - 1) We know that highest accessibility & complete is downtown. But people there have fewer children + lowest income are downtown.  On the horizon as rent increases,  the most precarious may be pushed out and replaced by people who can pay higher rents. 2) The lowest accessibility & most incomplete are suburban -- they are likely higher income. Interesting to note: one-parent families are more likely to be time poor -- and leaving in low access/incomplete suburbs puts more at risk. We know a think or 2 about single parents and jobs -- access to jobs was high where single parents were not. (Catherine, farber Paez paper). 3) Pockets of the suburbs have high access to care. The suburbs do something -- they have care amenities. ", " ")`
  `r word_comment("IDEAS DISCUSSED: regarding @fig-Fig9 - 2) The lowest accessibility & most incomplete are suburban -- they are likely higher income. Interesting to note: one-parent families are more likely to be time poor -- and leaving in low access/incomplete suburbs puts more at risk. We know a think or 2 about single parents and jobs -- access to jobs was high where single parents were not. (Catherine, farber Paez paper). ", ":")`.

 `r word_comment("IDEAS DISCUSSED: regarding @fig-Fig9 - 3) Pockets of the suburbs have high access to care. The suburbs do something -- they have care amenities. ", ":")`.

# Conclusions and Discussion

There seems to be a spatial mismatch where dwelling availability and affordability play an important role? Are there social housing programs for lower income households?
